SoK: Defending Against Web Application Attacks: From Research Approaches to Practical Tools

### 2014-11-15 docs/questioning.tex
from the BSD to Wordpress

For domain-specific language code injection attacks, mechanisms check 
the query before the inclusion of user input with the one
resulting after the inclusion of user input.
Two mechanisms that implement this approach for protection against {\sc SQL}
injection attacks,
{\sc sqlg}uard~\cite{BWS05} and
{\sc sql}check~\cite{SW06}, are quite similar
and detect the attack before a query reaches the
database (Point {\sc dbal}).
Contrary to {\sc sqlg}uard,
% mikepo: if others exist, cite them
%and other mechanisms,
{\sc sql}check has been
extensively tested in terms of accuracy,
as can be seen in Table~\ref{tab:comp}.
A disadvantage of these mechanisms is that the
application must be modified in every code fragment
that sends an {\sc sql} query to the database for execution.

@@

\noindent
This same application could allow users to lock their terminal,
but allow the unlocking either with the user's password or with
the administrator password (the 4.3 {\sc bsd} {\em lock} command
behaved in this peculiar way).
The corresponding query to verify the password on the locked
workstation would be as follows:

>>>>

For domain-specific language code injection attacks, mechanisms check 
the query before the inclusion of user input with the one
resulting after the inclusion of user input.
Two mechanisms that implement this approach for protection
against {\sc sql} injection attacks,
{\sc sqlg}uard~\cite{BWS05} and
{\sc sql}check~\cite{SW06}, are quite similar
and detect the attack before a query reaches the
database (Point {\sc dbal}).
Contrary to {\sc sqlg}uard,
% mikepo: if others exist, cite them
%and other mechanisms,
{\sc sql}check has been
extensively tested in terms of accuracy,
as can be seen in Table~\ref{tab:comp}.
A disadvantage of these mechanisms is that the
application must be modified in every code fragment
that sends an {\sc sql} query to the database for execution.

@@

\noindent
This same application could allow users to
login to the site using just their password via a custom login form
(like the ``Password only login" plugin of
Wordpress\footnote{\url{https://wordpress.org/plugins/password-only-login/}})
but allow the login either with the user's password or with
the administrator password. The corresponding query to verify
the password on the login form would be as follows:
